---
title: "Homework2"
format: html
editor: visual
---

## Task 1

```{r}
pre_bp = c(130, 128, 116, 124, 133, 134, 118, 126, 114, 127, 141, 138, 128, 140, 137, 131, 120, 128, 139, 135)
post_bp = c(114, 98, 113, 99, 107, 116, 113, 111, 119, 117, 101, 119, 130, 122, 106, 106, 124, 102, 117, 113)
patient = paste("Subject", 1:20, sep = "_")
diff_bp = post_bp - pre_bp
diff_mean = mean(diff_bp)

indices = which(diff_bp < 0)
indices
patient[indices]

pos_diffs = diff_bp[-indices]
```

4.  The mean difference in blood pressure from pre-treatment to post-treatment was found to be **`r diff_mean`**

5.  The subset of Subjects that had a higher blood pressure post-treatment were `r patient[-indices]`

6.  The mean difference in blood pressure post-treatment for those who saw an increase in blood pressure was found to be **`r mean(pos_diffs)`**.

## Task 2

```{r}
bp_dataframe = data.frame(patient, pre_bp, post_bp, diff_bp)

subset(bp_dataframe,diff_bp < 0)

bp_dataframe$low_bp = ifelse(bp_dataframe$post_bp < 120, TRUE, FALSE)
bp_dataframe

knitr::kable(bp_dataframe)
```

## Task 3

```{r}
pre = c(138, 135, 147, 117, 152, 134, 114, 121, 131, 130)
post = c(105, 136, 123, 130, 134, 143, 135, 139, 120, 124)
patient = paste("Subject", 1:10, sep = "_")
diffs = post - pre

placebo = data.frame(patient,pre,post,diffs)
placebo$low_bp = ifelse(placebo$post < 120, TRUE, FALSE)

new_list = list(treatment = bp_dataframe, placebo = placebo)

new_list[1]
new_list[[1]]
new_list$treatment

new_list$placebo[,2]
```

## Task 4

```{r}
new_list$treatment$status = character(20)
new_list$placebo$status = character(10)

for(i in seq_along(new_list$treatment$status)){
  ifelse(new_list$treatment$post_bp[i] <= 120, new_list$treatment$status[i] == "optimal",
         ifelse(new_list$treatment$post_bp[i] <= 130, new_list$treatment$status[i] == "borderline", new_list$treatment$status[i] == "high"))
}

for(i in seq_along(new_list$placebo$status)){
  ifelse(new_list$placebo$post[i] <= 120, new_list$placebo$status[i] == "optimal",
         ifelse(new_list$placebo$post[i] <= 130, new_list$placebo$status[i] == "borderline", new_list$placebo$status[i] == "high"))
}
```

## Task 5
I was unable to get to this part of the assignment and should have asked for an extension earlier. 